### 2015-03-14 technique.tex
updated the toolchain figure and some text

>>>>

We have implemented our approach in \whoop, a prototype infrastructure that combines static lockset analysis with state-of-the-art compilation and sequential verification techniques to (i) soundly analyse Linux kernel modules for data races and (ii) accelerate a plugged-in precise bug finder. Figure~\ref{fig:whoop}

\begin{figure*}
\centering
\includegraphics[width=.99\linewidth]{img/whoop.pdf}
\caption{The \textsc{Whoop} infrastructure, empowered by state-of-the-art compilation (Clang/LLVM and SMACK) and verification (Boogie and Corral) tools}
\label{fig:whoop}
\end{figure*}

\subsection{Static Pairwise Lockset Analysis}
\label{spla}
